Computing Exact Restricted Isometry Constants via\\ Mixed Integer Semidefinite Programming

### 2016-03-16 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
Rank instead of Rk since we never introduce it formally
added table with sizes of used matrices

\newcommand{\suchthat}{\,:\,}
\newcommand{\abs}[1]{\lvert{#1}\rvert}
\newcommand{\card}[1]{\lvert{#1}\rvert}
\newcommand{\define}{\coloneqq}
\newcommand{\enifed}{\eqqcolon}
\newcommand{\norm}[1]{\lVert{#1}\rVert}
\newcommand{\Norm}[2]{\lVert{#1}\rVert_{#2}}
\newcommand{\skal}[2]{\langle{#1},{#2}\rangle}
\newcommand{\order}[1]{O\left({#1}\right)}
\newcommand{\T}{^{\top}}
\newcommand{\Tr}{\text{Tr}}
\newcommand{\Rk}{\text{Rk}}
\newcommand{\vect}{\text{vec}}

@@

We use a testset consisting of 63 matrices of seven 
different types including band matrices, 
with band size three or five with entries within the band chosen uniformly in $\{0,1\}$, binary matrices with all entries chosen 
uniformly in $\{0,1\}$, Gaussian-distributed matrices and rank one 
matrices $A = aa\T$ with $N(0,1)$-distributed entries of $a$. In addition to these four types,
we also use three more with theoretical results on their restricted isometry
constants. These include matrices with 
$N(0, 1/m)$-distributed entries, with entries chosen uniformly in $\pm 1/\sqrt{m}$ and finally with distribution
\begin{equation}\nonumber
  A_{ij} = \begin{cases}
    + \sqrt{3/m} & \text{with probability } \frac{1}{6}, \\
    0 & \text{with probability } \frac{2}{3}, \\
    - \sqrt{3/m} & \text{with probability } \frac{1}{6}.
  \end{cases}
\end{equation}
For each type we used \mbox{MATLAB 8.3.0} to randomly generate nine
matrices of three different sizes with rows ranging from 15 to 30, columns
from 25 to 40 and order $k$ between three and five.

>>>>

\newcommand{\suchthat}{\,:\,}
\newcommand{\abs}[1]{\lvert{#1}\rvert}
\newcommand{\card}[1]{\lvert{#1}\rvert}
\newcommand{\define}{\coloneqq}
\newcommand{\enifed}{\eqqcolon}
\newcommand{\norm}[1]{\lVert{#1}\rVert}
\newcommand{\Norm}[2]{\lVert{#1}\rVert_{#2}}
\newcommand{\skal}[2]{\langle{#1},{#2}\rangle}
\newcommand{\order}[1]{O\left({#1}\right)}
\newcommand{\T}{^{\top}}
\newcommand{\Tr}{\text{Tr}}
\newcommand{\Rk}{\text{Rank}}
\newcommand{\vect}{\text{vec}}

@@

We use a testset consisting of 63 matrices of seven 
different types including band matrices, 
with band size three or five with entries within the band chosen uniformly in $\{0,1\}$, binary matrices with all entries chosen 
uniformly in $\{0,1\}$, Gaussian-distributed matrices and rank one 
matrices $A = aa\T$ with $N(0,1)$-distributed entries of $a$. In addition to these four types,
we also use three more with theoretical results on their restricted isometry
constants. These include matrices with 
$N(0, 1/m)$-distributed entries, with entries chosen uniformly in $\pm 1/\sqrt{m}$ and finally with distribution
\begin{equation}\nonumber
  A_{ij} = \begin{cases}
    + \sqrt{3/m} & \text{with probability } \frac{1}{6}, \\
    0 & \text{with probability } \frac{2}{3}, \\
    - \sqrt{3/m} & \text{with probability } \frac{1}{6}.
  \end{cases}
\end{equation}
For each type we used \mbox{MATLAB 8.3.0} to randomly generate nine
matrices of three different sizes with rows ranging from 15 to 30, columns
from 25 to 40 and order $k$ between three and five, see Table~\ref{matrixsizes}.

\begin{table} 
 \begin{scriptsize} \caption{Sizes of the used matrices, three matrices were
 randomly generated for each size} 
 \label{matrixsizes} 
 \begin{tabular*}{\linewidth}{@{}l@{\;\;\extracolsep{\fill}}rrrrrrrrr@{}}\toprule 
  & \multicolumn{3}{c}{1} & \multicolumn{3}{c}{2} & \multicolumn{3}{c}{3} \\ 
\cmidrule(r){2-4} \cmidrule{5-7}  \cmidrule(l){8-10}
type & $m$ & $n$ & $k$ & $m$ & $n$ & $k$ & $m$ & $n$ & $k$  \\ 
\midrule 
$N(0,1)$ & 15 & 30 & 5 & 25 & 35 & 4 & 30 & 40 & 3 \\
binary & 15 & 30 & 5 & 25 & 35 & 4 & 30 & 40 & 3 \\
band matrix & 30 & 30 & 5 & 35 & 35 & 4 & 40 & 40 & 3 \\
rank 1& 30 & 30 & 5 & 35 & 35 & 4 & 40 & 40 & 3 \\
$N(0,1/m)$ & 15 & 30 & 5 & 25 & 35 & 4 & 30 & 40 & 3 \\
$\pm 1/\sqrt{m}$ & 15 & 30 & 5 & 25 & 35 & 4 & 30 & 40 & 3 \\
$0, \pm \sqrt{3/m}$ & 15 & 30 & 5 & 25 & 35 & 4 & 30 & 40 & 3 \\
\bottomrule 
 \end{tabular*} 
 \end{scriptsize} 
 \end{table}
